Optimal (Multiway) Spatial Joins

### 2024-05-19 msj.tex
yufei

\todo{Rahul's result?}

@@

@@

\section{An $\bm{\Omega(n \log n)}$ Lower Bound} \label{app:lb}

>>>>

\todo{Rahul's result? No. Do it in later sections}

@@

Now that Theorem~\ref{thm:main-alg} offers a satisfactory $k$-SJ result in 2D space, it is natural to wonder whether the constraint on dimensionality 2 is necessary. The answer, interestingly, is --- to a great extent --- yes as far as $k \ge 3$ is concerned. Specifically, if the 3D version of the 3-SJ problem could be solved in $O(n \polylog n + \out)$ time, we would obtain an algorithm that detects the presence of a triangle (i.e., 3-clique) in a graph of $m$ edges in $O(m \polylog m)$ time (which would make a truly surprising breakthrough because the state of the art needs $O(m^{1.41})$ time \cite{ayz97}). This can be shown using an argument in \cite{kcko22}, which is included in Appendix~\ref{app:lb-cond} for self-containment.

@@

\section{An $\bm{\Omega(n \log n)}$ Lower Bound for 2-SJ} \label{app:lb}

\section{Hardness of 3-SJ in 3D Space} \label{app:lb-cond}
